---
title: "IGRAM"
author: "Ceylan Tanes - CHOP Microbiome Center"
date: \today
output: 
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  tidy=FALSE,
  cache=FALSE,
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  dpi=100,
  fig.width=6,
  fig.height=4,
  fig.align = "center"
  )
```

```{r child = 'igram_abx_preamble.Rmd'}
```


```{r}
s <- s %>%
  filter(visit %in% c("4M", "12M", "24M")) %>%
  droplevels()
```


## Batch effects 

```{r}
table(s$run, s$visit)
```


```{r}
summaries_df <- s %>%
  filter(visit %in% c("4M", "12M", "24M")) %>%
  #group_by(visit, comparison) %>%
  filter(!is.na(is_breastfed)) %>%
  do(adonisplus(., distmat=bc_rarefied, formula = distmat ~ visit + is_breastfed + run, sample_id_var = SampleID, perm=999)) %>%
  #ungroup() %>%
  filter(!term %in% c("Residuals", "Total")) %>%
  select(-sumsq) #%>%
  #mutate(fdr = p.adjust(p.value, method="BH"))

summaries_df %>% 
  pander(split.table=Inf, digits=2)
```



## Fig 1B

```{r}
s_abx_summary %>%
  group_by(SubjectID, visit, abx_name) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!visit %in% c("SS2_B", "SS2_WK1", "SS2_WK2", "SS2_WK3")) %>%
  
  mutate(abx_grouped = fct_lump(abx_name, n=9)) %>%
  mutate(abx_grouped = fct_collapse(abx_grouped, Other = c("Other", "unknown antibiotic", "Unknown antibiotic"))) %>%
  
  mutate(for_color = ifelse(abx_grouped %in% c("Amoxicillin", "Amoxicillin-Clavulanate"), "Amox", "Other")) %>%
  
  group_by(abx_grouped) %>%
  mutate(sample_size = n()) %>%
  ungroup() %>%
  mutate(abx_grouped = paste0(abx_grouped, " (", sample_size, ")")) %>%
  
  mutate(abx_grouped = fct_relevel(abx_grouped, "Other (45)", after=Inf)) %>%
  
  ggplot(aes(x=abx_age, fill=for_color)) +
    geom_histogram() +
    geom_vline(xintercept=4, linetype=2) +
    geom_vline(xintercept=12, linetype=2) +
    geom_vline(xintercept=24, linetype=2) +
    facet_wrap(~abx_grouped) +
    scale_x_continuous(breaks=seq(0,24,4)) +
    scale_fill_brewer(palette="Set1") +
    theme_bw() +
    theme(
      panel.grid = element_blank(),
      strip.background = element_blank()
    ) + 
    guides(fill="none") +
    labs(
      x = "Age (months)",
      y = "Number of antibiotics prescriptions"
    )
ggsave("igram_abx_Fig1B_abxSummary.pdf", height=4, width=5.5, useDingbats=F)
```


# Exposed vs non-exposed at each time point

4M, 12M and 24M samples are included in the analysis. 

```{r}
s_toTest <- s %>%
  filter(!is.na(SubjectID)) %>%
  filter(visit %in% c("4M", "12M", "24M")) %>%
  
  filter(SampleID != "I2.345.24M") %>% # there are two s345 24M time points. Manually removing one
  
  #select(SampleID, SubjectID, visit, age_at_visit, delivery_type, intrapartum_antibiotics, gest_age, feeding_type, is_breastfed,
  #       first_abx_exposure, abx_4M_any, abx_first_year_any, abx_2Y_any, abx_2Y_any_nonAmox, nonhost) %>%
  
  mutate(exposed_abx = dplyr::case_when(visit %in% "4M" ~ abx_4M_any, 
                                        visit %in% "12M" ~ abx_first_year_any, 
                                        visit %in% "24M" ~ abx_2Y_any,
                                        TRUE ~ NA) ) %>%
  
  mutate(is_breastfed = feeding_type %in% c("breastmilk", "mixed")) %>%
  mutate(is_breastfed = ifelse(is_breastfed, "BF", "no BF")) %>%
  mutate(is_breastfed = fct_rev(factor(is_breastfed))) %>%
  
  mutate(first_abx_exposure = fct_recode(first_abx_exposure, 
                                         Unexposed = "no abx",
                                         `Early exposure` = "before 4M",
                                         `Mid exposure` = "btw 4M and 12M",
                                         `Late exposure` = "after 12M")) %>%
  
  mutate(delivery_type = fct_collapse(delivery_type, `C-section`=c("C-Section with labor", "C-Section without labor"))) %>%
  
  droplevels()
  
  
s_toTest_expanded <- s_toTest %>%
  select(SampleID, SubjectID, visit, first_abx_exposure, is_breastfed, delivery_type, gest_age, intrapartum_antibiotics, Richness, Shannon, otu_counts) %>%
  mutate(comp_exposure_Early_exposure = first_abx_exposure %in% c("Unexposed", "Early exposure")) %>%
  mutate(comp_exposure_Mid_exposure = first_abx_exposure %in% c("Unexposed", "Mid exposure")) %>%
  mutate(comp_exposure_Late_exposure = first_abx_exposure %in% c("Unexposed", "Late exposure")) %>% 
  pivot_longer(cols=starts_with("comp_"), names_to="comparison", values_to="keep") %>% 
  filter(keep) %>% select(-keep) %>% 
  mutate(comparison = sub("comp_exposure_", "", comparison)) %>%
  mutate(comparison = gsub("_", " ", comparison)) 

pander(table(s_toTest$first_abx_exposure, s_toTest$visit))

s_toTest %>%
  select(SubjectID, first_abx_exposure) %>%
  unique() %>%
  pull(first_abx_exposure) %>%
  table()

ann_colors = list(
  first_abx_exposure = factor_palette(s_toTest$first_abx_exposure, viridis(length(levels(s_toTest$first_abx_exposure)), option="plasma", end=0.8) ),
  is_breastfed = factor_palette(s_toTest$is_breastfed, c("#59114D", "#297373") )
)

```

```{r}
addmargins(table(s_toTest$visit, s_toTest$is_breastfed, useNA = "ifany")) %>%
  pander(split.table=Inf)
```


```{r}
abx_stats <- s_abx_summary %>% 
  filter(SubjectID %in% s_toTest$SubjectID) %>%
  
  group_by(SubjectID, visit, abx_name) %>%
  slice(1) %>%
  ungroup() %>%
  
  group_by(SubjectID) %>%
  summarize(num_abx = n()) %>%
  ungroup() %>%
  
  mutate(is_multiple = num_abx > 1) 

abx_stats %>% pull(is_multiple) %>% mean()
abx_stats %>% pull(num_abx) %>% mean()
abx_stats %>% pull(num_abx) %>% sd()
```


```{r}
s_abx_summary %>% 
  filter(SubjectID %in% s_toTest$SubjectID) %>%
  left_join(s_toTest %>% select(SubjectID, first_abx_exposure) %>% unique(), by="SubjectID") %>%
  
  group_by(SubjectID, visit, abx_name, first_abx_exposure) %>%
  slice(1) %>%
  ungroup() %>%
  
  group_by(SubjectID, first_abx_exposure) %>%
  summarize(num_abx = n()) %>%
  ungroup() %>%
  
  group_by(first_abx_exposure) %>%
  summarize(mean_abx = mean(num_abx), sd_abx = sd(num_abx)) %>%
  ungroup() %>%
  
  pander(split.table=Inf, digits=2)
```

## Fig2A

```{r}
s_toTest %>%
  mutate(divide = ifelse(first_abx_exposure == "Unexposed", "Control", "Exposed samples")) %>%
  mutate(divide = factor(divide)) %>%
  mutate(relevant = ifelse(first_abx_exposure == "Early exposure" | 
           (first_abx_exposure == "Mid exposure" & visit %in% c("12M", "24M")) |
           (first_abx_exposure == "Late exposure" & visit %in% c("24M")),
           "C", "B")) %>%
  mutate(relevant = ifelse(first_abx_exposure=="Unexposed", "A", relevant)) %>%
  group_by(first_abx_exposure, visit, divide, relevant, is_breastfed) %>%
  summarize(num_breastfed = n()) %>%
  ungroup() %>%
  
  group_by(first_abx_exposure, visit, divide, relevant) %>%
  mutate(num_samples = sum(num_breastfed)) %>%
  ungroup() %>%
  
  filter(is_breastfed %in% "BF") %>%
  mutate(perc_breastfed = round(num_breastfed / num_samples * 100, digits=0)) %>%
  
  mutate(num_samples_text = paste0("n=", num_samples, "\nBF n=", num_breastfed, " (", perc_breastfed, "%)")) %>%
  #mutate(num_samples_text = paste0("n=", num_samples, "\n", " (", perc_breastfed, "% BF)")) %>%
  
  mutate(first_abx_exposure = fct_relabel(first_abx_exposure, function(x) sub(" exposure", "", x))) %>% 
  mutate(first_abx_exposure = fct_rev(first_abx_exposure)) %>%
  
  ggplot(aes(x=visit, y=first_abx_exposure, fill=relevant)) +
    geom_tile(height=0.95, width=0.95) +
    geom_text(aes(label=num_samples_text), size=4) +
    facet_grid(divide~., space = "free", scale = "free") +
    scale_fill_manual(values = c("#FFFFFF", "#B8B2AC", "#FC8268")) +
    theme_clean() +
    scale_y_discrete(expand = c(0,0)) +
    scale_x_discrete(expand = c(0,0)) +
    theme(
      axis.ticks = element_blank()
    ) +
    guides(fill = "none") +
    labs(
      y="Antibiotics exposure", x="Age"
    )
    
#ggsave("igram_abx_Fig2A_overview.pdf", height=3, width=3.5, useDingbats=F)
ggsave("igram_abx_Fig2A_overview.pdf", height=5, width=5.2, useDingbats=F)
```

Fisher's exact test on counts of exposed vs unexposed subjects who are breastfed or not breastfed.

```{r}
## check if unexposed subjects are more likely to be breastfed
s_toTest %>%
  
  group_by(visit, exposed_abx, is_breastfed) %>%
  summarize(num_breastfed = n()) %>%
  ungroup() %>%
  
  group_by(visit) %>%
  do(tidy(fisher.test(matrix(.$num_breastfed, nrow=2)))) %>%
  ungroup() %>%
  
  select(-method) %>%
  
  pander(split.table=Inf, digits=2)
```

```{r}
## check if unexposed subjects are more likely to be breastfed
s_toTest %>%
  
  group_by(visit, first_abx_exposure, is_breastfed) %>%
  summarize(num_breastfed = n()) %>%
  ungroup() %>%
  
  group_by(visit) %>%
  do(tidy(fisher.test(matrix(.$num_breastfed, nrow=2)))) %>%
  ungroup() %>%
  
  select(-method) %>%
  
  pander(split.table=Inf, digits=2)
```


## Supp Fig 3 Alpha diversity

```{r fig.height=6, fig.width=6}
s_toTest %>%
  gather("metric", "alpha", c("Richness", "Shannon")) %>%
  ggplot(aes(x=visit, y=alpha, color=first_abx_exposure, shape=is_breastfed)) +
    geom_boxplot(outlier.alpha=0) +
    geom_quasirandom(dodge.width=0.75, alpha=0.7) +
    scale_color_manual(values=ann_colors$first_abx_exposure) +
    scale_shape_manual(values=c(16,1)) +
    facet_wrap(~metric, ncol=1, scales="free_y") +
    theme_clean() +
    theme(
      aspect.ratio = 0.5
    ) +
    #guides(color=F) +
    labs(
      x="Age", color="Abx\nexposure", shape="Breastfed",
      y="Number of distinct species\nper 1,000 reads"
    )
ggsave("igram_abx_SuppFig3_alpha.pdf", width=8, height=5, useDingbats=F)
```


For each visit:
alpha ~ is_breastfed + first_abx_exposure
Each group is compared to the no-abx group


```{r}

summaries_df <- s_toTest_expanded %>%
  gather("metric", "alpha", c("Richness", "Shannon")) %>%
  #mutate(metric = fct_recode(metric, Richness="richness", Shannon="shannon")) %>%
  group_by(metric, visit, comparison) %>%
  do(tidy(lm(alpha ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  #filter(!grepl("Intercept", term)) %>%
  mutate(term = sub("first_abx_exposure", "no abx - ", term)) %>%
  mutate(term = gsub("TRUE", "", term)) %>%
  
  group_by(metric, term) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()


## Calculate percent decrease in richness for breastfed babies
summaries_df %>% 
  #filter(metric == "Richness") %>% 
  filter(grepl("Intercept|is_breastfed", term)) %>%
  mutate(term = sub("\\(Intercept\\)", "Intercept", term)) %>%
  select(visit, comparison, metric, term, estimate) %>%
  pivot_wider(names_from="term", values_from="estimate") %>%
  mutate(perc_change = is_breastfedBF / Intercept) %>%
  group_by(metric, visit) %>%
  summarize(mean(perc_change)) %>%
  ungroup()


summaries_df %>% 
  #filter(metric == "Richness") %>% 
  filter(comparison == "Early exposure") %>%
  filter(visit == "12M")

summaries_df %>%
  filter(!grepl("Intercept", term)) %>%
  pander(split.table=Inf, digits=2)
```



## Differential abundance

```{r}
props_toTest <- summed_props[,s_toTest$SampleID] %>%
  as.data.frame() %>% 
  rownames_to_column("Taxa") %>% 
  pivot_longer(-Taxa, names_to="SampleID", values_to="props") %>%
  #right_join(s_toTest, by="SampleID")  %>%
  group_by(Taxa) %>%
  mutate(perc_present = sum(props > 0)/n()) %>%
  mutate(mean_prop = mean(props)) %>%
  ungroup() %>%
  filter(mean_prop > 0.01) %>%
  filter(Taxa != "Bacteria") %>%
  filter(!grepl("phage", Taxa)) %>%
  
  mutate(props_original = props) %>%
  mutate(props = props + min(filter(., props>0)$props) / 10) %>%
  mutate(props_log = log10(props)) %>%
  mutate(clr_trans = log(props) - mean(log(props)))

props_toTest_expanded <- props_toTest %>%
  right_join(s_toTest_expanded, by="SampleID") %>%
  mutate(counts = props_original * otu_counts)

props_toTest <- props_toTest %>%
  right_join(s_toTest, by="SampleID")
```



## Test the effect of multiple antibiotics

```{r}
abx_stats <- s_abx_summary %>% 
  filter(SubjectID %in% s_toTest$SubjectID) %>%
  
  group_by(SubjectID, visit, abx_name) %>%
  slice(1) %>%
  ungroup() %>%
  select(SubjectID, abx_age) %>%
  
  left_join(select(s_toTest, SubjectID, visit, age_at_visit), by="SubjectID") %>%
  
  filter(abx_age < age_at_visit) %>%
  
  group_by(SubjectID, visit) %>%
  count() %>%
  ungroup() %>%
  
  right_join(select(s_toTest, SubjectID, visit), by=c("SubjectID", "visit")) %>%
  mutate(n = ifelse(is.na(n), 0, n))

summaries_df <- props_toTest %>%
  left_join(abx_stats, by=c("SubjectID", "visit")) %>%
  #filter(first_abx_exposure != "Unexposed") %>%
  
  group_by(Taxa, visit) %>%
  do(tidy(lm(props_log ~ is_breastfed + n, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))


props_toTest %>%
  left_join(abx_stats, by=c("SubjectID", "visit")) %>%
  filter(Taxa %in% c("Actinobacteria Bifidobacterium bifidum")) %>%
  mutate(n_factor = as.factor(n)) %>%
  ggplot(aes(x=n, y=props)) +
    #geom_boxplot() +
    geom_quasirandom(aes(shape=is_breastfed), width=0.25, alpha=0.8) +
    geom_smooth(method="lm", color="black") +
    scale_y_continuous(labels=scales:::percent, trans="log10", limits = c(0.000001, 2), breaks = c(0.00001, 0.001, 0.01, 0.1, 1)) +
    scale_shape_manual(values=c(16,1)) +
    facet_wrap(~visit) +
    theme_clean() +
    theme(
      aspect.ratio = 1
    ) +
    labs(
      x = "Number of antibiotic prescriptions", shape="",
      y = "Relative abundance of\nBifidobacterium bifidum"
    )
ggsave("igram_abx_SuppFig3_diff_ab_dose.pdf", height=3, width=8, useDingbats=F)
```



```{r}
# Check for normality of log transformed values
props_toTest %>%
  ggplot(aes(x=props_log)) +
    geom_histogram() +
    facet_wrap(~Taxa)

props_toTest %>%
  group_by(Taxa) %>%
  do(tidy(shapiro.test(.$props_log))) %>%
  ungroup() %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  View()
```


## Supp table 2

For each visit: props_log ~ is_breastfed + first_abx_exposure
In this comparison we are comparing the "first abx exposure" group to the control group with no antibiotics at each time point. 

```{r}
library(DHARMa)
tidy_lm_temp <- function(lm_test) {
  sim_fmp <- simulateResiduals(lm_test, refit=T) 
  tidy(lm_test) %>%
    mutate(dispersion_pvalue = tidy(testDispersion(sim_fmp))$p.value)
}

summaries_df <- props_toTest_expanded %>%
  
  group_by(Taxa, visit, comparison) %>%
  do(tidy(lm(props_log ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))

write.table(summaries_df, "igram_abx_SuppTable2.txt", row.names=F, quote=F, sep='\t')
```

```{r}
## tried glm per reviewer suggestion
tidy_glm <- function(glm_test) {
  tidy(glm_test) %>%
    mutate(converged = glm_test$converged) %>%
    mutate(deviance = deviance(glm_test)) %>%
    mutate(residual_df = glm_test$df.residual) %>%
    mutate(dispersion_parameter = sum((glm_test$weights * glm_test$residuals^2)[glm_test$weights > 0])/glm_test$df.residual)
}

summaries_df_glm <- props_toTest_expanded %>%
  group_by(Taxa, visit, comparison) %>%
  do(tidy_glm(glm(cbind(counts, otu_counts-counts) ~ is_breastfed + first_abx_exposure, data=., family="quasibinomial"))) %>%
  
  # alternative way to run the tests
  #do(tidy(glm(props ~ is_breastfed + first_abx_exposure, data=., family="quasibinomial", weights=otu_counts))) %>%
  
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))
```


```{r eval=F}
library(betareg)
summaries_df_beta <- props_toTest_expanded %>%
  group_by(Taxa, visit, comparison) %>%
  do(tidy(betareg(props ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term)) %>%
  
  filter(component == "mean")
```

```{r}
summaries_df_clr <- props_toTest_expanded %>%
  
  group_by(Taxa, visit, comparison) %>%
  do(tidy(lm(clr_trans ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))
```



```{r}
summaries_df_combined <- summaries_df %>%
  select(Taxa, visit, comparison, term, estimate_lm_log=estimate, std.error_lm_log=std.error, p.value_lm_log=p.value, fdr_lm_log=fdr) %>%
  left_join(select(summaries_df_clr, Taxa, visit, comparison, term, estimate_lm_clr=estimate, std.error_lm_clr=std.error, p.value_lm_clr=p.value, fdr_lm_clr=fdr)) %>%
  left_join(select(summaries_df_beta, Taxa, visit, comparison, term, estimate_lm_beta=estimate, std.error_lm_beta=std.error, p.value_lm_beta=p.value, fdr_lm_beta=fdr)) %>%
  left_join(select(summaries_df_glm, Taxa, visit, comparison, term, estimate_lm_glm=estimate, std.error_lm_glm=std.error, p.value_lm_glm=p.value, fdr_lm_glm=fdr))

write.table(summaries_df_combined, file="igram_abx_diff_ab_comparison.tsv", sep='\t', quote=F, row.names=F)
```

```{r fig.width=12, fig.height=17}
bind_rows(
  summaries_df %>% mutate(method = "lm log"),
  summaries_df_clr %>% mutate(method = "lm clr"),
  summaries_df_beta %>% mutate(method = "beta"),
  summaries_df_glm %>% mutate(method = "glm"),
) %>%
  mutate(term = sub("Unexposed - ", "", term)) %>%
  mutate(term = sub("is_breastfedBF", "breastfeeding", term)) %>%
  mutate(isSig = ifelse(fdr < 0.1, "q<0.1", "q>0.1")) %>%
  mutate(method = factor(method, levels=c("lm log", "lm clr", "beta", "glm"))) %>%
  mutate(term = fct_relevel(factor(term), "Late exposure", after=Inf)) %>%
  
  mutate(isSig = ifelse(fdr < 0.1, "q<0.1", "q>0.1")) %>%
  ggplot(aes(x=estimate, y=Taxa, color=method, shape=isSig)) +
    geom_vline(xintercept=0, linetype=2) +
    geom_pointrange(aes(xmin=estimate-std.error, xmax=estimate+std.error), position = position_dodge(width = 0.5)) +
    #geom_text(aes(x=7, label=p_label), vjust=0.76, hjust=1, color="black") +
    facet_grid(visit~term, scales="free_x") +
    #scale_color_manual(values=c(rev(as.character(ann_colors$study_day[-1])), as.character(wes_palette("GrandBudapest1"))[2], as.character(wes_palette("Royal1"))[1])) +
    scale_shape_manual(values=c(16,1)) +
    theme_clean() +
    guides(colour = guide_legend(reverse=T)) +
    labs(
      x="Estimated log difference between groups",
      y="", color="", shape=""
    )

ggsave("igram_abx_diff_ab_comparison.pdf", height=15, width=10, useDingbats=F)
```

```{r fig.width=12, fig.height=17}
bind_rows(
  summaries_df %>% mutate(method = "lm\nlog"),
  summaries_df_clr %>% mutate(method = "lm\nclr"),
  summaries_df_beta %>% mutate(method = "beta"),
  summaries_df_glm %>% mutate(method = "glm"),
) %>%
  filter(fdr < 0.1) %>%
  mutate(method = factor(method, levels=c("lm\nlog", "lm\nclr", "beta", "glm"))) %>%
  mutate(shape_by = ifelse(term == "is_breastfedBF", "Breastfeeding", "Antibiotics")) %>%
  mutate(direction = ifelse(estimate > 0, "Up", "Down")) %>%
  
  ggplot(aes(x=method, y=Taxa, color=direction)) +
    geom_point() +
    #scale_shape_manual(values=c("\u25E3","\u25E5")) +
    #scale_fill_manual(values=c("gray80", "steelblue1", "steelblue3","steelblue4")) +
    scale_color_manual(values=c("deepskyblue", "tomato1")) +
    facet_grid(visit+shape_by~comparison) +
    theme_bw() +
    theme(
      strip.background = element_blank()
    ) +
    labs(
      x="Method", y="", 
      color="Direction\nof change", shape="Term\nin model"
    )
ggsave("igram_abx_diff_ab_comparison2.pdf", height=20, width=7.5, useDingbats=F)
```

```{r fig.width=12, fig.height=17}
p <- bind_rows(
  summaries_df %>% mutate(method = "lm\nlog"),
  summaries_df_clr %>% mutate(method = "lm\nclr"),
  summaries_df_beta %>% mutate(method = "beta"),
  summaries_df_glm %>% mutate(method = "glm"),
) %>%
  filter(fdr < 0.1) %>%
  mutate(method = factor(method, levels=c("lm\nlog", "lm\nclr", "beta", "glm"))) %>%
  mutate(shape_by = ifelse(term == "is_breastfedBF", "Breastfeeding", "Antibiotics")) %>%
  mutate(direction = ifelse(estimate > 0, "Up", "Down")) %>%
  
  ggplot(aes(x=method, y=Taxa, color=direction, shape=shape_by)) +
    geom_point(size = 8) +
    scale_shape_manual(values=c("\u25E3","\u25E5")) +
    #scale_fill_manual(values=c("gray80", "steelblue1", "steelblue3","steelblue4")) +
    scale_color_manual(values=c("deepskyblue", "tomato1")) +
    facet_grid(visit~comparison) +
    theme_clean() +
    labs(
      x="Method", y="", 
      color="Direction\nof change", shape="Term\nin model"
    )
cairo_pdf("igram_abx_diff_ab_comparison3.pdf", family="Arial Unicode MS", 8,15)
p
dev.off()

#ggsave("igram_abx_diff_ab_comparison3.pdf", height=15, width=10, useDingbats=F)
```


## Fig 2D

```{r fig.width=14, fig.height=8}
taxa_of_interest <- props_toTest %>%
  select(Taxa, mean_prop) %>%
  unique() %>%
  separate(Taxa, remove = F, into=c("Phylum", "Species"), extra="merge") %>%
  ## we want B. theta to make the list because it was statistically significant
  #mutate(mean_prop = ifelse(Species == "Bacteroides thetaiotaomicron", 0.3, mean_prop)) %>%
  arrange(-mean_prop) %>%
  group_by(Phylum) %>%
  slice(1:3) %>%
  ungroup() %>%
  filter(!Taxa %in% "Proteobacteria Enterobacteriaceae") %>%
  mutate(Phylum = ifelse(Phylum %in% c("Proteobacteria", "Verrucomicrobia"), "Proteobacteria and\nVerrucomicrobia", Phylum)) %>%
  select(Taxa, Phylum)

summaries_df %>% 
  right_join(taxa_of_interest, by="Taxa") %>%
  mutate(term = ifelse(grepl("Unexposed", term), "Abx effect", term)) %>%
  mutate(term = sub("is_breastfed", "Breastfeeding", term)) %>%
  mutate(term = factor(term)) %>%
  mutate(term = fct_rev(term)) %>%
  
  mutate(Taxa = gsub(" ", "\n", Taxa)) %>%
  
  mutate(comparison = sub(" exposure", "", comparison)) %>%
  mutate(comparison = factor(comparison, levels=c("Late", "Mid", "Early"))) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*",
    fdr < 0.1 ~ "+"
  )) %>%
  mutate(sig_color = ifelse(abs(estimate) > 0.8, "A", "B")) %>%
  
  ggplot(aes(x=visit, y=comparison, fill=estimate)) +
    geom_tile() +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    facet_grid(term ~ Taxa) +
    scale_fill_gradient2(low="#053061", mid="#F7F7F7", high="#67001F", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    theme_clean() +
    theme(
      aspect.ratio=1
    ) +
    guides(color="none") +
    labs(
      y="Antibiotics exposure", fill="Log10\nestimated\nmean\ndifference",
      x="Age"
    )
ggsave("igram_abx_Fig2D_diffAb.pdf", height=4, width=14, useDingbats=F)
```


## Supp Fig 2

For each visit: props_log ~ is_breastfed * first_abx_exposure
In this comparison we are comparing the "first abx exposure" group to the control group with no antibiotics at each time point. 

```{r}
summaries_df <- props_toTest_expanded %>%
  
  group_by(Taxa, visit, comparison) %>%
  do(tidy(lm(props_log ~ is_breastfed * first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))
```


```{r fig.width=14, fig.height=8}
summaries_df %>% 
  right_join(taxa_of_interest, by="Taxa") %>%
  mutate(term = ifelse(grepl(":", term), "Interaction", term)) %>%
  mutate(term = ifelse(grepl("Unexposed", term), "Abx effect", term)) %>%
  mutate(term = sub("is_breastfed", "Breastfeeding", term)) %>%
  mutate(term = factor(term)) %>%
  
  mutate(Taxa = gsub(" ", "\n", Taxa)) %>%
  
  mutate(comparison = sub(" exposure", "", comparison)) %>%
  mutate(comparison = factor(comparison, levels=c("Late", "Mid", "Early"))) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*",
    fdr < 0.1 ~ "+"
  )) %>%
  mutate(sig_color = ifelse(abs(estimate) > 1, "A", "B")) %>%
  #mutate(sig_color = ifelse(abs(estimate) > 2.5, "A", "B")) %>%
  
  ggplot(aes(x=visit, y=comparison, fill=estimate)) +
    geom_tile() +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    facet_grid(term ~ Taxa) +
    scale_fill_gradient2(low="#053061", mid="#F7F7F7", high="#67001F", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    theme_clean() +
    theme(
      aspect.ratio=1
    ) +
    labs(
      y="Antibiotics exposure", fill="Log10\nestimated\nmean\ndifference",
      x="Age"
    )
ggsave("igram_abx_SuppFig2_subsample_BF_abx_interaction.pdf", height=4, width=14, useDingbats=F)
```


For each visit, comparison and intrapartum abx status: props_log ~ is_breastfed + first_abx_exposure

```{r}
summaries_df <- props_toTest_expanded %>%
  filter(intrapartum_antibiotics %in% c("Yes", "No")) %>%
  
  group_by(Taxa, visit, comparison, intrapartum_antibiotics) %>%
  do(tidy(lm(props_log ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit, comparison, intrapartum_antibiotics) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))
```


```{r fig.width=14, fig.height=8}
summaries_df %>% 
  right_join(taxa_of_interest, by="Taxa") %>%
  mutate(term = ifelse(grepl(":", term), "Interaction", term)) %>%
  mutate(term = ifelse(grepl("Unexposed", term), "Abx effect", term)) %>%
  mutate(term = sub("is_breastfed", "Breastfeeding", term)) %>%
  mutate(term = factor(term)) %>%
  mutate(term = fct_rev(term)) %>%
  
  mutate(Taxa = gsub(" ", "\n", Taxa)) %>%
  
  mutate(comparison = sub(" exposure", "", comparison)) %>%
  mutate(comparison = factor(comparison, levels=c("Late", "Mid", "Early"))) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*",
    fdr < 0.1 ~ "+"
  )) %>%
  mutate(sig_color = ifelse(abs(estimate) > 1, "A", "B")) %>%
  
  ggplot(aes(x=visit, y=comparison, fill=estimate)) +
    geom_tile() +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    facet_grid(term + intrapartum_antibiotics ~ Taxa) +
    scale_fill_gradient2(low="#053061", mid="#F7F7F7", high="#67001F", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    theme_clean() +
    theme(
      aspect.ratio=1
    ) +
    guides(color="none") +
    labs(
      y="Antibiotics exposure", fill="Log10\nestimated\nmean\ndifference",
      x="Age"
    )
ggsave("igram_abx_SuppFig2_subsample_intrapartum_abx.pdf", height=6, width=14, useDingbats=F)
```


For each visit, comparison and delivery type: props_log ~ is_breastfed + first_abx_exposure

```{r}
summaries_df <- props_toTest_expanded %>%
  filter(!is.na(delivery_type)) %>%
  
  group_by(Taxa, visit, comparison, delivery_type) %>%
  do(tidy(lm(props_log ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit, comparison, delivery_type) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))
```


```{r fig.width=14, fig.height=8}
summaries_df %>% 
  right_join(taxa_of_interest, by="Taxa") %>%
  mutate(term = ifelse(grepl(":", term), "Interaction", term)) %>%
  mutate(term = ifelse(grepl("Unexposed", term), "Abx effect", term)) %>%
  mutate(term = sub("is_breastfed", "Breastfeeding", term)) %>%
  mutate(term = factor(term)) %>%
  mutate(term = fct_rev(term)) %>%
  
  mutate(Taxa = gsub(" ", "\n", Taxa)) %>%
  
  mutate(comparison = sub(" exposure", "", comparison)) %>%
  mutate(comparison = factor(comparison, levels=c("Late", "Mid", "Early"))) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*",
    fdr < 0.1 ~ "+"
  )) %>%
  mutate(sig_color = ifelse(abs(estimate) > 0.8, "A", "B")) %>%
  
  ggplot(aes(x=visit, y=comparison, fill=estimate)) +
    geom_tile() +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    facet_grid(term + delivery_type ~ Taxa) +
    scale_fill_gradient2(low="#053061", mid="#F7F7F7", high="#67001F", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    theme_clean() +
    theme(
      aspect.ratio=1
    ) +
    guides(color="none") +
    labs(
      y="Antibiotics exposure", fill="Log10\nestimated\nmean\ndifference",
      x="Age"
    )
ggsave("igram_abx_SuppFig2_subsample_delivery_type.pdf", height=6, width=14, useDingbats=F)
```


For each visit, comparison: props_log ~ gestational_age + is_breastfed + first_abx_exposure


```{r}
summaries_df <- props_toTest_expanded %>%
  filter(!is.na(gest_age)) %>%
  mutate(gest_age = gest_age / 7) %>%
  
  group_by(Taxa, visit, comparison) %>%
  do(tidy(lm(props_log ~ gest_age + is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))

```


```{r fig.width=14, fig.height=8}
summaries_df %>% 
  right_join(taxa_of_interest, by="Taxa") %>%
  mutate(term = ifelse(grepl(":", term), "Interaction", term)) %>%
  mutate(term = ifelse(grepl("Unexposed", term), "Abx effect", term)) %>%
  mutate(term = sub("is_breastfed", "Breastfeeding", term)) %>%
  mutate(term = sub("gest_age", "Gestational age", term)) %>%
  
  mutate(term = factor(term)) %>%
  mutate(term = fct_rev(term)) %>%
  
  mutate(Taxa = gsub(" ", "\n", Taxa)) %>%
  
  mutate(comparison = sub(" exposure", "", comparison)) %>%
  mutate(comparison = factor(comparison, levels=c("Late", "Mid", "Early"))) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*",
    fdr < 0.1 ~ "+"
  )) %>%
  mutate(sig_color = ifelse(abs(estimate) > 0.8, "A", "B")) %>%
  
  ggplot(aes(x=visit, y=comparison, fill=estimate)) +
    geom_tile() +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    facet_grid(term ~ Taxa) +
    scale_fill_gradient2(low="#053061", mid="#F7F7F7", high="#67001F", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    theme_clean() +
    theme(
      aspect.ratio=1
    ) +
    guides(color="none") +
    labs(
      y="Antibiotics exposure", fill="Log10\nestimated\nmean\ndifference",
      x="Age"
    )
ggsave("igram_abx_SuppFig2_covariate_gestational_age.pdf", height=4, width=14, useDingbats=F)
```

## Fig 2B

```{r fig.width=8}
temp <- s_toTest %>%
  pcoaplus(bc_rarefied) 
  
temp_centroids <- temp %>%
  group_by(first_abx_exposure, visit) %>%
  summarize(Axis.1 = mean(Axis.1), Axis.2 = mean(Axis.2)) %>%
  ungroup() %>%
  mutate(is_breastfed = "zAverage")

temp %>%
  ggplot(aes(x=Axis.1, y=Axis.2, color=first_abx_exposure)) +
  geom_point(aes(shape=is_breastfed), alpha=0.5) +
  geom_point(data=temp_centroids, aes(x=Axis.1, y=Axis.2, color=first_abx_exposure, shape=is_breastfed), size=1.5, stroke=1.2) +
  stat_ellipse() +
  scale_shape_manual(values=c(16,1,8)) + 
  facet_wrap(~visit) +
  scale_color_manual(values=ann_colors$first_abx_exposure) +
  theme_clean_pcoa() +
  guides(alpha="none") +
  labs(
    x = attr(temp, "axislabel")[1], y = attr(temp, "axislabel")[2],
    color="Abx exposure", shape="Breastfed")

ggsave("igram_abx_Fig2B.pdf", height=3, width=8,useDingbats=F)
```

## Supp Fig 1A

```{r fig.width=8}
temp_centroids <- temp %>%
  group_by(is_breastfed, visit) %>%
  summarize(Axis.1 = mean(Axis.1), Axis.2 = mean(Axis.2)) %>%
  ungroup() %>%
  mutate(for_shape = "Centroids")

temp %>%
  mutate(for_shape = "Data") %>%
  ggplot(aes(x=Axis.1, y=Axis.2, color=is_breastfed, shape=for_shape)) +
  geom_point(alpha=0.4) +
  geom_point(data=temp_centroids, aes(x=Axis.1, y=Axis.2, color=is_breastfed, shape=for_shape), size=1.5, stroke=1.2) +
  stat_ellipse(alpha=1) +
  scale_shape_manual(values=c(8, 16)) + 
  facet_grid(first_abx_exposure~visit) +
  scale_color_manual(values=ann_colors$is_breastfed) +
  theme_clean_pcoa() +
  guides(alpha="none") +
  labs(
    x = attr(temp, "axislabel")[1], y = attr(temp, "axislabel")[2],
    color="Breastfeeding", shape="")

ggsave("igram_abx_SuppFig1A_pcoa_BF.pdf", height=4.5, width=4.5,useDingbats=F)
```


For each visit and abx exposure group, compare it to the no abx group.
distmat ~ is_breastfed + first_abx_exposure

```{r}
summaries_df <- s_toTest_expanded %>%
  group_by(visit, comparison) %>%
  do(adonisplus(., distmat=bc_rarefied, formula = distmat ~ is_breastfed + first_abx_exposure, sample_id_var = SampleID, perm=999)) %>%
  ungroup() %>%
  filter(!term %in% c("Residuals", "Total")) %>%
  select(-sumsq) %>%
  
  group_by(term) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  pander(split.table=Inf, digits=2)
```



For each visit and abx exposure group, compare it to the no abx group.
distmat ~ is_breastfed * first_abx_exposure

```{r}
summaries_df <- s_toTest_expanded %>%
    group_by(visit, comparison) %>%
    do(adonisplus(., distmat=bc_rarefied, formula = distmat ~ is_breastfed * first_abx_exposure, sample_id_var = SampleID, perm=999)) %>%
    ungroup() %>%
  filter(!term %in% c("Residuals", "Total")) %>%
  select(-sumsq) %>%
  
  group_by(term) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  pander(split.table=Inf, digits=2)
```



# Exposed vs non-exposed at each time point (amox subjects only)

## Supp Fig 2

4M, 12M and 24M samples are included in the analysis. 

```{r}
s_toTest <- s %>%
  filter(!is.na(SubjectID)) %>%
  filter(visit %in% c("4M", "12M", "24M")) %>%
  
  filter(SampleID != "I2.345.24M") %>% # there are two s345 24M time points. Manually removing one

  #select(SampleID, SubjectID, visit, age_at_visit, delivery_type, intrapartum_antibiotics, gest_age, feeding_type,
  #       first_abx_exposure, abx_4M_any, abx_first_year_any, abx_2Y_any, abx_2Y_any_nonAmox, nonhost) %>%

  mutate(is_breastfed = feeding_type %in% c("breastmilk", "mixed")) %>%
  mutate(is_breastfed = ifelse(is_breastfed, "BF", "no BF")) %>%
  mutate(is_breastfed = fct_rev(factor(is_breastfed))) %>%
  
  mutate(first_abx_exposure = fct_recode(first_abx_exposure, 
                                         Unexposed = "no abx",
                                         `Early exposure` = "before 4M",
                                         `Mid exposure` = "btw 4M and 12M",
                                         `Late exposure` = "after 12M")) %>%
  
  mutate(delivery_type = fct_collapse(delivery_type, `C-section`=c("C-Section with labor", "C-Section without labor"))) %>%
  
  droplevels()


amox_only_subjects <- s %>%
  filter(!is.na(SubjectID)) %>%
  filter(visit %in% c("4M", "12M", "24M")) %>%
  
  filter(SampleID != "I2.345.24M") %>% # there are two s345 24M time points. Manually removing one
  
  filter(!abx_2Y_any_nonAmox) %>%
  pull(SubjectID) %>%
  unique() %>% 
  as.character()
  
  
s_toTest <- s_toTest %>%
  filter(SubjectID %in% amox_only_subjects)


s_toTest_expanded <- s_toTest %>%
  select(SampleID, SubjectID, visit, first_abx_exposure, is_breastfed, otu_counts) %>%
  mutate(comp_exposure_Early_exposure = first_abx_exposure %in% c("Unexposed", "Early exposure")) %>%
  mutate(comp_exposure_Mid_exposure = first_abx_exposure %in% c("Unexposed", "Mid exposure")) %>%
  mutate(comp_exposure_Late_exposure = first_abx_exposure %in% c("Unexposed", "Late exposure")) %>% 
  pivot_longer(cols=starts_with("comp_"), names_to="comparison", values_to="keep") %>% 
  filter(keep) %>% select(-keep) %>% 
  mutate(comparison = sub("comp_exposure_", "", comparison)) %>%
  mutate(comparison = gsub("_", " ", comparison)) 

pander(table(s_toTest$first_abx_exposure, s_toTest$visit))




s_toTest %>%
  select(SubjectID, first_abx_exposure) %>%
  unique() %>%
  pull(first_abx_exposure) %>%
  table()
```



```{r}
addmargins(table(s_toTest$visit, s_toTest$is_breastfed, useNA = "ifany")) %>%
  pander(split.table=Inf)
```



```{r}
props_toTest <- summed_props[,s_toTest$SampleID] %>%
  as.data.frame() %>% 
  rownames_to_column("Taxa") %>% 
  pivot_longer(-Taxa, names_to="SampleID", values_to="props") %>%
  #right_join(s_toTest, by="SampleID")  %>%
  group_by(Taxa) %>%
  mutate(perc_present = sum(props > 0)/n()) %>%
  mutate(mean_prop = mean(props)) %>%
  ungroup() %>%
  filter(mean_prop > 0.01) %>%
  filter(Taxa != "Bacteria") %>%
  filter(!grepl("phage", Taxa)) %>%
  
  mutate(props_original = props) %>%
  mutate(props = props + min(filter(., props>0)$props) / 10) %>%
  mutate(props_log = log10(props))


props_toTest_expanded <- props_toTest %>%
  right_join(s_toTest_expanded, by="SampleID") %>%
  mutate(counts = props_original * otu_counts)

props_toTest <- props_toTest %>%
  right_join(s_toTest, by="SampleID")
```




For each visit: props_log ~ is_breastfed + first_abx_exposure
In this comparison we are comparing the "first abx exposure" group to the control group with no antibiotics at each time point. 

```{r}
summaries_df <- props_toTest_expanded %>%
  
  group_by(Taxa, visit, comparison) %>%
  do(tidy(lm(props_log ~ is_breastfed + first_abx_exposure, data=.))) %>%
  ungroup() %>%
  filter(!grepl("Intercept", term)) %>%
  #mutate(term = sub("study_day", "BL - ", term)) %>%
  group_by(term, visit, comparison) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup() %>%
  
  mutate(term = sub("first_abx_exposure", "Unexposed - ", term)) %>%
  mutate(term = gsub("TRUE", "", term))
```


```{r fig.width=14, fig.height=8}
summaries_df %>% 
  right_join(taxa_of_interest, by="Taxa") %>%
  mutate(term = ifelse(grepl("Unexposed", term), "Abx effect", term)) %>%
  mutate(term = sub("is_breastfed", "Breastfeeding", term)) %>%
  mutate(term = factor(term)) %>%
  mutate(term = fct_rev(term)) %>%
  
  mutate(Taxa = gsub(" ", "\n", Taxa)) %>%
  
  mutate(comparison = sub(" exposure", "", comparison)) %>%
  mutate(comparison = factor(comparison, levels=c("Late", "Mid", "Early"))) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*",
    fdr < 0.1 ~ "+"
  )) %>%
  mutate(sig_color = ifelse(abs(estimate) > 0.8, "A", "B")) %>%
  #mutate(sig_color = ifelse(abs(estimate) > 2, "A", "B")) %>%
  
  ggplot(aes(x=visit, y=comparison, fill=estimate)) +
    geom_tile() +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    facet_grid(term ~ Taxa) +
    scale_fill_gradient2(low="#053061", mid="#F7F7F7", high="#67001F", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    theme_clean() +
    theme(
      aspect.ratio=1
    ) +
    guides(color="none") +
    labs(
      y="Antibiotics exposure", fill="Log10\nestimated\nmean\ndifference",
      x="Age"
    )
ggsave("igram_abx_SuppFig2_amoxOnly.pdf", height=4, width=14, useDingbats=F)
```

